Learning Libraries of Subroutines for Neurally--Guided Bayesian Program Learning

### 2018-05-18 nips_2018.tex
itemize contributions

Prior work on program learning has largely assumed a fixed, hand-engineered DSL,
both in classic symbolic program learning approaches (e.g., Metagol:~\cite{muggleton2015meta},
FlashFill:~\cite{gulwani2011automating}),
neural approaches  (e.g., RobustFill:~\cite{devlin2017robustfill}), and hybrids of neural and
symbolic methods (e.g., Neural-guided deductive search:~\cite{ngds}, DeepCoder:~\cite{balog2016deepcoder}).
A notable exception is the EC algorithm~\cite{Dechter:2013:BLV:2540128.2540316},
which also learns a library of subroutines.
We were motivated by EC, and go beyond it and other prior work through the following contributions:
(1) We show how to learn-to-learn programs in an expressive Lisp-like programming language;
(2) We give an algorithm for learning DSLs,
built on a formalism known as Fragment Grammars~\cite{tim};
and (3) We give a hierarchical Bayesian framing of
the problem that
allows a joint inference of the DSL and recognition model.

>>>>

Prior work on program learning has largely assumed a fixed, hand-engineered DSL,
both in classic symbolic program learning approaches (e.g., Metagol:~\cite{muggleton2015meta},
FlashFill:~\cite{gulwani2011automating}),
neural approaches  (e.g., RobustFill:~\cite{devlin2017robustfill}), and hybrids of neural and
symbolic methods (e.g., Neural-guided deductive search:~\cite{ngds}, DeepCoder:~\cite{balog2016deepcoder}).
A notable exception is the EC algorithm~\cite{Dechter:2013:BLV:2540128.2540316},
which also learns a library of subroutines.
We were motivated by EC, and go beyond it and other prior work through the following contributions:

\begin{itemize}
  \setlength\itemsep{0}
  \item We show how to learn-to-learn programs in an expressive Lisp-like programming language;
  \item We give an algorithm for learning DSLs, built on a formalism known
    as Fragment Grammars~\cite{tim}; and 
  \item We give a hierarchical Bayesian framing of the problem that allows a
    joint inference of the DSL and recognition model.
\end{itemize}
